A Switching Planner for Combined Task and Observation Planning

### 2011-02-09 subarchitectures/planner.sa/trunk/src/latex/AAAI11/switching.tex
more switching text

\noindent where $\$(T_i)$ (resp. $\hat\$(T_i)$) is a 
relatively small positive (negative) numeric quantity\footnote{Small
relative to rewards from the original process model.} which captures
the utility the agent receives for correctly (incorrectly) rejecting
an assumption. A disconfirm action can only be executed once, and
except in the applicability of that dual corresponds to a
self-transformation
%%
We only consider {\em relevant} assumptions and their duals when
constructing the abstract model.  If \switchAction\ is the action that
switched the system to a DT session, then an assumption
$\assumptiveS{i}$ is {\em relevant} if it is necessary for the outcome
of \switchAction\ to be determined. Continuing our simplified example,
if the trace is:

% Furthermore, if \switchAction\ is the action that switched the system
% to a DT session, then an assumption $\assumptiveS{i}$ is only {\em
% active} if
% \switchAction\ is not applicable in the sequential model unless
% $\assumptiveS{i}$ is scheduled in the trace prefix
% to \switchAction. We only include the duals of active assumptions in
% DT sessions. Continuing our simplified example, if the trace is:

@@

Given \switchAction, we also include another self-transition action
$\actions.\poss(\switchAction)$, the \emph{goal action} with the
reward property:

@@

Execution of either a disconfirmation or the goal action returns
control to a sequential session, which then continues from the
underlying belief-state. Turning to the detail of rewards, in our
integrated system these are sourced from a motivational subsystem. In
this paper, for $\assumptiveDT{i}$ actions we set $\$(x)$ to be a
small positive constant, and have $\hat\$(x)= - \$(x)(1 - \prob) /
\prob$ where $\prob$ is the probability that $x$ is true. For
$\actions.\poss(\switchAction)$ actions we have $\hat\$(x)= -
\$(x)\prob/(1-\prob)$.

@@

As we are aiming to keep the decision theoretic session fast, we try
to keep the state space of the abstract problem as small as
possible. In a deterministic-action POMDP, the state space size is
determined by two factors: the number of non-zero states in the
initial belief-state and the number of executable actions. As
determining the relevance of an action for a given goal in in general
a hard problem, we concentrate on keeping the number of uncertain
facts as low as possible without losing important information about
the sensing goal.

We perform the abstraction of the belief space by first constructing
an $(\pp{:init})$ declaration which only contains relevant assumptions
from the trace -- e.g., (Fig.\ref{fig:abstraction-b}) gives an
example, where diamonds are probabilistic terms, and circles are
atomic and/or conjunctive.
%%
For each excluded atom, we compute the {\em entropy} of the active
assumptions, {\em conditional} on that atom. Intuitively, lower
entropy indicates an atom gives better information about
assumptions. Facts are iteratively added to the belief-state in
increasing order according to that measure until the belief space size
reaches a predefined limit or no more atoms that reduce the entropy
can be added (Fig.\ref{fig:abstraction-c}).

>>>>

\noindent where $\$(T_i)$ (resp. $\hat\$(T_i)$) is a 
relatively small positive (negative) numeric quantity\footnote{Small
relative to rewards from the original process model.} which captures
the utility the agent receives for correctly (incorrectly) rejecting
an assumption.
%%
In terms of action physics, a disconfirm action can only be executed
once, and otherwise is modelled as self-transformation.
%%
We only consider {\em relevant} assumptions when constructing the
abstract model.  If \switchAction\ is the action that switched the
system to a DT session, then an assumption $\assumptiveS{i}$ is {\em
relevant} if it is necessary for the outcome of \switchAction\ to be
determined.  Continuing our simplified example, if the trace is:

@@

Given \switchAction, we also include another once-only self-transition
action $\actions.\poss(\switchAction)$, the \emph{confirmation action}
with the reward property:

@@

Execution of either a disconfirmation or the confirmation action
returns control to a sequential session, which then continues from the
underlying belief-state.

Turning to the detail of (dis-)confirmation rewards, in our integrated
system these are sourced from a motivational subsystem. In this paper,
for $\assumptiveDT{i}$ actions we set $\$(x)$ to be a small positive
constant, and have $\hat\$(x)= - \$(x)(1 - \prob) /
\prob$ where $\prob$ is the probability that $x$ is true. For
$\actions.\poss(\switchAction)$ actions we have $\hat\$(x)= -
\$(x)\prob/(1-\prob)$.

@@

%%  the size of the state space
%% is determined by two factors: the number of non-zero states in the
%% initial belief-state, and the number of actions. Determining
%% action reachability is intractable, as is determining their relevance
%% to goal achievement.

%% As we are aiming to keep the decision theoretic session fast, we try
%% to keep the state space of the abstract problem as small as
%% possible. In a deterministic-action POMDP, the state space size is
%% determined by two factors: the number of non-zero states in the
%% initial belief-state and the number of executable actions. As
%% determining the relevance of an action for a given goal in in general
%% a hard problem, we concentrate on keeping the number of uncertain
%% facts as low as possible without losing important information about
%% the sensing goal.

In order to guarantee fast DT sessions, planning occurs for a small
abstract problem. In our setting, where the underlying decision
process has a deterministic action model, a significant cause of
problem largeness is due to the number of states that occur with
non-zero probability in the underlying belief-state. In posing a small
abstract process for a DT session, we construct an abstract
belief-state that is chiefly characterised by facts related to the
current trace. In that abstraction, instances of operator or sense
declarations whose specification mentions an excluded fact are not
available.
%%
In detail, we first construct an $(\pp{:init})$ declaration which only
contains relevant assumptions from the trace -- e.g.,
(Fig.\ref{fig:abstraction-b}) gives an example, where diamonds are
probabilistic terms, and circles are atomic and/or conjunctive.
%%
For each excluded atom, we compute the {\em entropy} of the active
assumptions, {\em conditional} on that atom. Intuitively, lower
entropy indicates an atom gives better information about
assumptions. Facts are iteratively added to the belief-state in
increasing order according to that measure until the belief space size
reaches a predefined limit (Fig.\ref{fig:abstraction-c}).

%%  or no more atoms that reduce the entropy
%% can be added
